---
title: "The factors that associate with nest size"
author: "lintong_deng"
date: "2024-04-04"
output: html_document
---

![human's "nest"](https://th.bing.com/th/id/R.fc5abbb075fe3c7333d4bb7519ab7337?rik=Z2ibg31i0LrJlw&riu=http%3a%2f%2fwww.blazzinghouse.com%2fwp-content%2fuploads%2f2011%2f06%2fNew-Giant-Bird-Nest-for-Breeding-Ideas-e1307329552214.jpg&ehk=JqJ1xF4zVgPxw99SonK6hD8kOP4sJ4zAMyo9%2fahzlDU%3d&risl=&pid=ImgRaw&r=0)



![real nest](https://th.bing.com/th/id/OIP.QcgstxBY0eK5dFlRFMEydAHaHa?rs=1&pid=ImgDetMain)

```{r}
library(readxl)

data <- read_excel("E:/R_output/Supporting_Data_Passerine_Nests.xlsx")
```


factor 1: Body mass

Outer_volume..cm3 ~ Body_mass..g

```{r,warning=FALSE}
# 移除包含NA值的行
data_clean <- na.omit(data)

# 提取数值型数据并转换为数值型
Outer_volume <- as.numeric(data_clean$Outer_volume..cm3)
Body_mass <- as.numeric(data_clean$Body_mass..g)

# 使用 cor.test() 函数进行相关性检验
cor_test_out_body_mass<- cor.test(Outer_volume, Body_mass)

# 查看相关性检验的结果
print(cor_test_out_body_mass)
```



factor 2: clutch size

Inner_volume..cm3 ~ Clutch_size 

```{r,warning=FALSE}
# Check data types
str(data_clean$Inner_volume..cm3)
str(data_clean$Clutch_size)
# chr`Inner volume
# num`Clutch size

# Check for missing values in the data
sum(is.na(data_clean$Inner_volume..cm3))
sum(is.na(data_clean$Clutch_size))
# 0
# No missing values found for both

# Convert the Inner_volume..cm3 column to numeric
data_clean$Inner_volume..cm3 <- as.numeric(data_clean$Inner_volume..cm3)

# Check the data type after conversion
str(data_clean$Inner_volume..cm3)
```


```{r}
# Calculate the correlation between Inner_volume..cm3 and Clutch_size
cor_test_in_clutch_size <- cor.test(data_clean$Inner_volume..cm3, data_clean$Clutch_size)

# Print the result
print(cor_test_in_clutch_size)
```


factor 3:temperature
Outer_volume..cm3 ~ Mean_temperature

```{r,warning=FALSE}
# Check data types
str(data_clean$Outer_volume..cm3)
str(data_clean$Mean_temperature)
# chr`
# num`

# Check for missing values in the data
sum(is.na(data_clean$Outer_volume..cm3))
sum(is.na(data_clean$Mean_temperature))
# 0
# No missing values found for both

# Convert the Outer_volume..cm3 column to numeric
data_clean$Outer_volume..cm3 <- as.numeric(data_clean$Outer_volume..cm3)

# Check the data type after conversion
str(data_clean$Outer_volume..cm3)
```


```{r}
# Perform correlation test using the cor.test() function
cor_test_out_mean_T <- cor.test(data_clean$Outer_volume..cm3, data_clean$Mean_temperature)

# View the results of the correlation test
print(cor_test_out_mean_T)
```



factor 4:predation threat (associated with the various factors of bio-geographical distribution)



①Insularity is binary rather than continuous, so we can use a t-test to examine the difference in observed values between two groups of samples.

```{r,warning=FALSE}
# Calculate the lower and upper quartiles and IQR (remove missing values)
Q1 <- quantile(data_clean$Outer_volume..cm3, 0.25, na.rm = TRUE)
Q3 <- quantile(data_clean$Outer_volume..cm3, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1

# Calculate the upper and lower limits for outliers
lower_limit <- Q1 - 1.5 * IQR
upper_limit <- Q3 + 1.5 * IQR

# Remove outliers
data_clean <- data_clean[data_clean$Outer_volume..cm3 >= lower_limit & data_clean$Outer_volume..cm3 <= upper_limit, ]

# Load R package
library(ggplot2)

# Use ggplot2 to draw a boxplot comparing Outer Volume between Insular and Non-insular
ggplot(data_clean, aes(x = as.factor(Insularity), y = Outer_volume..cm3, fill = as.factor(Insularity))) +
  geom_boxplot(alpha = 0.7) +  # Set the transparency of the boxplot
  labs(x = "Insularity", y = "Outer Volume", title = "Comparison of Outer Volume by Insularity") +
  scale_fill_manual(values = c("0" = "blue", "1" = "red")) +  # Set the fill colors
  theme_minimal()  # Use a minimal theme
```

```{r}
# Perform t-test to compare Outer Volume between different levels of Insularity
t_test_insularity <- t.test(Outer_volume..cm3 ~ Insularity, data = data_clean)

# Print the results of the t-test
print(t_test_insularity)
```

②rock
"Loc_rock" is binary rather than continuous, so we can use a t-test to examine the difference in observed values between two groups of samples.

Visualization - Boxplot

```{r,warning=FALSE}
# Use ggplot2 to draw a boxplot comparing Outer Volume between nests located on rocks and nests not located on rocks
ggplot(data_clean, aes(x = as.factor(Loc_rock), y = Outer_volume..cm3, fill = as.factor(Loc_rock))) +
  geom_boxplot(alpha = 0.7) +  # Set the transparency of the boxplot
  labs(x = "Location - Rock", y = "Outer Volume", title = "Comparison of Outer Volume by whether the nest is located on rock") +
  scale_fill_manual(values = c("0" = "blue", "1" = "red")) +  # Set the fill colors
  theme_minimal()  # Use a minimal theme
```


```{r}
# Perform t-test for Loc_rock
t_test_rock <- t.test(Outer_volume..cm3 ~ Loc_rock, data = data_clean)
print(t_test_rock)
```

